%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

\thispagestyle{plain} % No headers, just page numbers

I would like to thank the people who directly or indirectly participated in the development of this thesis as well as to those who provided me with help and encouragement needed during this journey.

First of all, I would like to thank my director, Dr. Lijun Qian, for guiding me while developing the project as well as for allowing me the chance to work in WICOMLAB with all my wonderful peers. 

I would also like to thank my teammates of the WICOMLAB for the interests, ideas they have been able to contribute. Especially to Mr. Yuzhong Yan, who helped me with debugging and fixing all the errors I could have during the implementation time as well as with contributing with ideas for accomplishing a better project.

Last, and not least, to my friends from Cascajal Foundation who have helped me clear when necessary and supported in many ways I can't appreciate enough; to Dr. Heladio Ibarguen and Family, who have listened to all of my problems and have made me see solutions with their comments; and my mother, thanks for listening to me and supporting me through difficult times even from the distance.

\pagebreak{}

\ifx true false
\vspace*{\fill}
\begin{center}
A.M.D.G.
\end{center}
\vspace*{\fill}
\pagebreak{}
\fi
